Acceleration of Global Search by Implementing Dual Estimates for Lipschitz Constant\thanks{This research was supported by the Russian Science Foundation, project No.\,16-11-10150.}

### 2019-09-12 2019/NUMTA_Barkalov/LNCS/numta19.tex
8 pages and vector figures

%Russian
A numerical comparison of the algorithms was carried out by solving several series of problems generated by the GKLS generator \cite{Gaviano2003}. This generator of multiextremal functions is widely used to compare global optimization methods (see, for example, \cite{Barkalov2018,Paulavicius2014,Sergeyev2015}). In this study, six series each containing 100 problems of dimensions $N = 3,4,5$ were solved. For each dimension, \textit{Simple} and \textit{Hard} problems were generated, differing in the size of the attraction region for local extremums and global extremum.
The problem was considered solved if the method conducted the next trial in sequence at a point that was in the $\delta$-neighborhood of the global minimizer $y^\ast$, 
i.e. $\left\|y^k-y^\ast\right\| <\delta\left\|b-a\right\|$, where  $a$ and $b$ are the boundaries of the search domain $D$.

@@

\begin{figure}
\begin{minipage}{0.5\linewidth}
\center{\includegraphics[width=1.0\linewidth]{Operating_characteristic_gklss_4.png} \\ (a)}
\end{minipage}
\hfill
\begin{minipage}{0.5\linewidth}
\center{\includegraphics[width=1.0\linewidth]{Operating_characteristic_gklsh_4.png} \\ (b)}
\end{minipage}
\caption{Operational characteristics for GKLS \textit{Simple} (a) and \textit{Hard} (b) classes, $N=4$.}
\label{oper4}
\end{figure}

@@

\begin{figure}
\begin{minipage}{0.5\linewidth}
\center{\includegraphics[width=1.0\linewidth]{Operating_characteristic_gklss_5.png} \\ (a)}
\end{minipage}
\hfill
\begin{minipage}{0.5\linewidth}
\center{\includegraphics[width=1.0\linewidth]{Operating_characteristic_gklsh_5.png} \\ (b)}
\end{minipage}
\caption{Operational characteristics for GKLS \textit{Simple} (a) and \textit{Hard} (b) classes, $N=5$.}
\label{oper5}
\end{figure}

>>>>

%Russian
A numerical comparison of the algorithms was carried out by solving several series of problems generated by the GKLS generator \cite{Gaviano2003}. This generator of multiextremal functions is widely used to compare global optimization methods (see, for example, \cite{Barkalov2018,Sergeyev2006,Sergeyev2015}). In this study, six series each containing 100 problems of dimensions $N = 3,4,5$ were solved. For each dimension, \textit{Simple} and \textit{Hard} problems were generated, differing in the size of the attraction regions for local extremums and global extremum.
The problem was considered solved if the method conducted the trial at a point that was in the $\delta$-neighborhood of the global minimizer $y^\ast$, 
i.e. $\left\|y^k-y^\ast\right\| <\delta\left\|b-a\right\|$, where  $a$ and $b$ are the boundaries of the search domain $D$.

@@

\begin{figure}
\begin{minipage}{0.47\linewidth}
\center{\includegraphics[width=1.0\linewidth]{Operating_characteristic_gklss_4.pdf} {\scriptsize \\ (a)}}
\end{minipage}
\hfill
\begin{minipage}{0.47\linewidth}
\center{\includegraphics[width=1.0\linewidth]{Operating_characteristic_gklsh_4.pdf} {\scriptsize \\ (b)}}
\end{minipage}
\caption{Operational characteristics for GKLS \textit{Simple} (a) and \textit{Hard} (b) classes, $N=4$.}
\label{oper4}
\end{figure}

@@

\begin{figure}
\begin{minipage}{0.47\linewidth}
\center{\includegraphics[width=1.0\linewidth]{Operating_characteristic_gklss_5.pdf} {\scriptsize \\ (a)}}
\end{minipage}
\hfill
\begin{minipage}{0.47\linewidth}
\center{\includegraphics[width=1.0\linewidth]{Operating_characteristic_gklsh_5.pdf} {\scriptsize \\ (b)}}
\end{minipage}
\caption{Operational characteristics for GKLS \textit{Simple} (a) and \textit{Hard} (b) classes, $N=5$.}
\label{oper5}
\end{figure}
